# Extract Population Data {#prep}

```{r load_raster,cache=TRUE,include=FALSE}
kenya_population <- raster("../../WorldPop/Kenya~/KEN_popmap15adj_v2b.tif")
malawi_population <- raster("../../WorldPop/Malawi~/MWI_ppp_2015_adj_v2.tif")
# tanzania_population <- raster("../../WorldPop/United~/TZA_popmap15adj_v2b.tif")
zambia_population <- raster("../../WorldPop/Zambia~/ZMB_ppp_v2c_2015_UNadj.tif")
```

To extract the population data, the sampling areas need to unified first. In the next step, the data gets extracted via the `prepare_raster_of_sampling_area`. Here, we make use of the `fasterize` package which is much faster in turning `SpatialPolygons` into raster files than the original `rasterize` function of the `raster` package. Finally, we aggregate the extracted data to a 1 and a 5 kilometer grid. The 5 km grid is shown in the following graphs.  


```{r popextractaggr,cache=TRUE}
# unify
# dar_unified <- gUnaryUnion(dar_bins_6)

lusaka_unified <- gUnaryUnion(lusaka_bins)

nairobi_unified <- gUnaryUnion(nairobi_bins)

# kenya_unified <- gUnaryUnion(kenya_sampling_bins)

# northern_tanzania_unified <- gUnaryUnion(northern_tanzania_sampling_bins)

# southern_tanzania_unified <- gUnaryUnion(southern_tanzania_sampling_bins)

malawi_unified <- gUnaryUnion(maw_sampling_bin)

zambia_unified <- gUnaryUnion(zambia_sampling_bin)

# extract
# dar_population <- 
#   prepare_raster_of_sampling_area(tanzania_population,dar_unified)

lusaka_population <- 
  prepare_raster_of_sampling_area(zambia_population,lusaka_unified)

nairobi_population <- 
  prepare_raster_of_sampling_area(kenya_population,nairobi_unified)

# kenya_population <- 
#   prepare_raster_of_sampling_area(kenya_population,kenya_unified)
# 
# northern_tanzania_population <- 
#   prepare_raster_of_sampling_area(tanzania_population,
#                                   northern_tanzania_unified)
# 
# southern_tanzania_population <- 
#   prepare_raster_of_sampling_area(tanzania_population,
#                                   southern_tanzania_unified)

malawi_population <- 
  prepare_raster_of_sampling_area(malawi_population,malawi_unified)

zambia_population <- 
  prepare_raster_of_sampling_area(zambia_population,zambia_unified)

# aggregate
# dar_population_1k <- aggregate(dar_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
# dar_population_5k <- aggregate(dar_population,fact=50,fun=sum,na.rm=TRUE) # 5 km

lusaka_population_1k <- aggregate(luska_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
lusaka_population_5k <- aggregate(luska_population,fact=50,fun=sum,na.rm=TRUE) # 5 km

nairobi_population_1k <- aggregate(nairobi_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
nairobi_population_5k <- aggregate(nairobi_population,fact=50,fun=sum,na.rm=TRUE) # 5 km

# kenya_population_1k <- aggregate(kenya_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
# kenya_population_5k <- aggregate(kenya_population,fact=50,fun=sum,na.rm=TRUE) # 5 km
# 
# northern_tanzania_population_1k <- 
#   aggregate(northern_tanzania_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
# northern_tanzania_population_5k <- 
#   aggregate(northern_tanzania_population,fact=50,fun=sum,na.rm=TRUE) # 5 km
# 
# southern_tanzania_population_1k <- 
#   aggregate(southern_tanzania_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
# southern_tanzania_population_5k <- 
#   aggregate(southern_tanzania_population,fact=50,fun=sum,na.rm=TRUE) # 5 km 

malawi_population_1k <- aggregate(malawi_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
malawi_population_5k <- aggregate(malawi_population,fact=50,fun=sum,na.rm=TRUE) # 5 km

zambia_population_1k <- aggregate(zambia_population,fact=10,fun=sum,na.rm=TRUE) # 1 km 
zambia_population_5k <- aggregate(zambia_population,fact=50,fun=sum,na.rm=TRUE) # 5 km


```


```{r extract,cache=TRUE}

# dar_bins_6 <- add_population(dar_bins_6,dar_population)
lusaka_bins <- add_population(lusaka_bins,luska_population)
nairobi_bins <- add_population(nairobi_bins,nairobi_population)

# kenya_bins <- add_population(kenya_sampling_bins,kenya_population)
# northern_tanzania_sampling_bins <- 
#   add_population(northern_tanzania_sampling_bins,northern_tanzania_population)
# southern_tanzania_sampling_bins <- 
#   add_population(southern_tanzania_sampling_bins,southern_tanzania_population)
maw_sampling_bin <- add_population(maw_sampling_bin,malawi_population)
zambia_sampling_bin <- add_population(zambia_sampling_bin,zambia_population)

```



```{r rasterggplotfunction,out.width="100%",echo=FALSE,cache=TRUE}


values_vector<-c(1,6,21,51,101,201)
values_vector<-log(c(0,100,seq(1000,100000,length.out = 5))+1)

values_vector<-log(c(0,100,1000,10000,20000,50000,100000,250000)+1)

ggplot_raster<-function(raster,title,values_vector,legend=FALSE,poly=NULL) {

  raster<-getValues(raster) %>% 
  data.frame(values=.) %>% 
  mutate(values=sapply(log(values),function(x) {
    if (is.na(x)) return(NA)
    t1 <- (x < values_vector)
    if (all(!t1)) return((values_vector %>% 
    max() %>% 
    exp()*2) %>% 
  log)
    values_vector[which(t1) %>% min]
  })) %>% 
    unlist() %>% 
  setValues(raster,.) 
  
  
values_vector_label <- 
  c(0,
    paste0("<",(exp(values_vector[2:length(values_vector)])-1)/1e3),
    paste0(">=",max((exp(values_vector)-1)/1e3)))
  
  g1 <- gplot(raster) +
    geom_raster(aes(fill=value),interpolate = FALSE) +
    # scale_fill_viridis_c() +
    coord_equal() +
    theme_map() +
    ggtitle(title) + 
  scale_fill_gradientn(name="Population in 1,000",
                       breaks = c(values_vector,(values_vector %>% 
                                                   max() %>% 
                                                   exp()*2) %>% 
                                    log),
                       colors=c("#8c510a",'#d73027','#fdae61','#fee090',
                                '#ffffbf','#e0f3f8','#abd9e9','#74add1',"#1a9850") %>% rev,
                       # mid = "#ffffbf",
                       # low ="#4575b4",
                       # high = '#7f0000',
                       labels=values_vector_label) +
  guides(fill = guide_legend(reverse=TRUE))
  
  if (!is.null(poly)) {
    poly$id<-1:length(poly)
    g1 <- g1 + 
    geom_polygon(data = poly %>% 
                   fortify(region="id"),
                 aes(x=long,y=lat,group=group),
                 fill=NA,color="black",alpha=0.5)
  }
  if (legend) return(g1)
  
  g1 + 
    guides(fill=FALSE)
}


  



```

```{r cityraster1,echo=FALSE,out.width="100%",fig.cap="Population in a 5 kilometer grid.",cache=TRUE}
grid.arrange(
  ggplot_raster(nairobi_population_5k,"Nairobi",values_vector,poly=nairobi_bins),
  ggplot_raster(luska_population_5k,"Lusaka",values_vector,poly=lusaka_bins),
  cowplot::get_legend(
    ggplot_raster(nairobi_population_5k,
                  "",
                  values_vector,
                  TRUE) +
      guides(fill=guide_legend(direction = "horizontal",
                               title.position = "top"))),
  layout_matrix=matrix(c(rep(c(1,2),4),3,3),ncol=2,byrow=TRUE))
```



```{r citiesraster2,out.width="100%",echo=FALSE,fig.cap="Population in a 5 kilometer grid.",cache=TRUE}
grid.arrange(
  ggplot_raster(malawi_population_5k,"Malawi",values_vector,
                poly = maw_sampling_bin),
  ggplot_raster(zambia_population_5k,"Zambia",values_vector,
                poly=zambia_sampling_bin),
  cowplot::get_legend(ggplot_raster(nairobi_population_5k,"",values_vector,TRUE) +
                      guides(fill=guide_legend(direction = "horizontal",
                                               title.position = "top"))),
  
  layout_matrix=matrix(c(rep(c(1,2),4),3,3),ncol=2,byrow=TRUE))
```



